---
title: "Machine Learning Course Project"
author: "J. Hagedorn"
date: "February 7, 2016"
output: html_document
---

## Background

We will be using data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants who were asked to perform barbell lifts correctly and incorrectly in 5 different ways. 

Our goal is to develop a model to predict the manner in which individuals performed a weight-lifting exercise (recorded in the `train$classe` variable).

More information is available from the [website here](http://groupware.les.inf.puc-rio.br/har) (*see the section on the Weight Lifting Exercise Dataset*). 


## Data

First, we'll load the data:

```{r}
train <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv")

test <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv")
```

## Building the Model
You may use any of the other variables to predict with. You should create a report describing how you built your model, 

## Cross Validation
how you used cross validation, 

## Out-of-Sample Error
what you think the expected out of sample error is, 

## Notes on Choices
and why you made the choices you did. 

## Prediction
You will also use your prediction model to predict 20 different test cases. 

```{r}

```

Publish using [gh-pages](https://help.github.com/articles/creating-pages-with-the-automatic-generator/)